The State of Debugging for RxJS\\``Debugging of RxJS-Based Applications''

### 2020-11-16 slides.tex
Updates from Overleaf

\begin{frame}[fragile]{Scope}
    \begin{columns}[T]
        \begin{column}{.4\linewidth}

            \begin{vfilleditems}
                \item Five \textbf{Interviews}\vspace{1em}
                \item General \textbf{Experience} with Reactive Programming\vspace{0.5em}
                \item What do you \textbf{like}?\vspace{0.5em}
                \item What do you \textbf{dislike}?
        	\end{vfilleditems}
        \end{column}
        \begin{column}{.4\linewidth}
            \begin{vfilleditems}
                \item Five War Story \textbf{Reports}\vspace{1em}
        		\item Recall a specific \textbf{challenging} debugging situation?\vspace{0.5em}
        		\item How did you \textbf{solve} it?
        	\end{vfilleditems}
        \end{column}
    \end{columns}
\end{frame}

@@

\note[itemize] {
    \item Lengthy answers
    \item Repeating themes
    \item RP is awesome for composing complex data flows
    \item That aside
    \item Debugging is hard
    \item Unsatisfying traditional debuggers
    \item Most often manual trace logs
    \item Or code extraction to to external tools
}

@@

\note[itemize] {
    \item Work on a concrete prototype
    \item Find solution for manual code modification scenarios
    \item Without manual intervention required
    \item Validate effectiveness in another study iteration
    \item One more thing...
}

\begin{frame}[fragile]{Sneak Preview}
    \begin{figure}[H]
        \centering
        \includegraphics[height=0.6\textheight]{figures/tweet-rxjs-debugging-extension.png}
        \caption{\tiny{Source: \url{https://twitter.com/swissmanu/status/1313412280072232960}}}
    \end{figure}
\end{frame}

\note[itemize] {
    \item Small sneak preview
    \item Things are progressing
    \item Thank you for your time and attention!
}

@@

>>>>

\begin{frame}[fragile]{Scope}
    \begin{columns}[T]
        \begin{column}{.4\linewidth}
            \begin{itemize}
                \item Five \textbf{Interviews}\vspace{1em}
                \begin{itemize}
                    \item General \textbf{Experience} with Reactive Programming\vspace{0.7em}
                    \item What do you \textbf{like}?\vspace{0.7em}
                    \item What do you \textbf{dislike}?
                \end{itemize}
        	\end{itemize}
        \end{column}
        \begin{column}{.4\linewidth}
            \begin{itemize}
                \item Five War Story \textbf{Reports}\vspace{1em}
                \begin{itemize}
            		\item Recall a specific \textbf{challenging} debugging situation?\vspace{0.7em}
            		\item How did you \textbf{solve} it?
        		\end{itemize}
        	\end{itemize}
        \end{column}
    \end{columns}
\end{frame}

@@

\note[itemize] {
    \item Repeating themes
    \item Debugging is hard
    \item Unsatisfying traditional debuggers
    \item Most often manual trace logs
    \item Or code extraction to to external tools
}

@@

\note[itemize] {
    \item Work on a concrete prototype
    \item Find solution for manual code modification scenarios
    \item Without manual intervention required
    \item Validate effectiveness in another study iteration
}

@@

\begin{frame}[fragile]{Future Work PoC: Add Probe}
    \begin{figure}[H]
        \centering
        \includegraphics[height=0.6\textheight]{figures/tweet-rxjs-debugging-extension.png}
        \caption{\tiny{Source: \url{https://twitter.com/swissmanu/status/1313412280072232960}}}
    \end{figure}
\end{frame}

\begin{frame}[fragile]{Future Work PoC: Monitor}
    \begin{figure}[H]
        \centering
        \includegraphics[height=0.7\textheight]{figures/backup-screenshots/step5-2.png}
        \caption{Empty Monitor Pane (right)}
    \end{figure}
\end{frame}

\begin{frame}[fragile]{Future Work PoC: Output}
    \begin{figure}[H]
        \centering
        \includegraphics[height=0.7\textheight]{figures/backup-screenshots/step8.png}
        \caption{Monitor Pane with Output (right)}
    \end{figure}
\end{frame}
